What is happening on Twitter? A framework for student research projects with tweets

### 2020-09-11 Rmd/jse-special-issue-2020-october.Rmd
minor text edits

We developed research goals with students in a series of discussions. As trainees began their senior research projects, we spoke in detail about both their research interests and goals and their experience with data analysis software.

Student experience with statistical software varies. In our statistics department, 
most students learn elementary R computing skills through class assignments. Some 
students, by concentrating in computer science, learn other data analysis software 
packages, such as Python. 
Those who do undergraduate statistics research often learn advanced topics in R
computing, such as R package assembly, documentation, and testing. Many develop 
expertise in linux computing and cluster computing, too.

One of our two students had extensive experience in statistical computing. In 
addition to R computing skills, she also worked in Python and excelled in shell scripting. 
She first learned Python in computer science courses. Our second student had 
extensive experience with R from his statistics courses. His background 
enabled him to write an R package as part of his senior project. To encourage 
further development of R computing skills in our two students, we guided them 
towards the online books "R for Data Science" [@wickham2016r] and "Advanced R" [@wickham2019advanced].

@@

Student interests vary, and students' ability to articulate research goals 
may be limited. An initial brainstorming session may clarify their interests and encourage 
them to think critically about goals under the time constraints of their academic schedules. 
Additionally, we anticipate that sharing completed student project reports will guide student 
thinking about the scope of possible projects (Supplementary files).

>>>>

We developed research goals with students in a series of brainstorming sessions and discussions. 
As trainees began their senior 
research projects, we spoke in detail about both their research interests and goals and their 
experience with data analysis software. When possible, we encouraged them to incorporate their 
existing academic interests into their senior research projects.

In our statistics department, most students learn elementary R computing skills through class 
assignments. Some students, by concentrating in computer science, learn other data analysis software 
packages, such as Python. 
Those who do undergraduate statistics research often learn advanced topics in R
computing, such as R package assembly, documentation, and testing. Many develop 
expertise in linux computing and cluster computing, too.

One of our two students had extensive experience in statistical computing. In 
addition to R computing skills, she also worked in Python and excelled in shell scripting. 
She first learned Python in computer science courses. Our second student had 
extensive experience with R from his statistics courses. His background 
enabled him to write an R package as part of his senior project. To encourage 
further development of R computing skills in our two students, we guided them 
towards the free, online books "R for Data Science" [@wickham2016r] and "Advanced R" [@wickham2019advanced].

@@

Our two students had diverse interests, and, initially, they had little experience in 
articulating research goals. We engaged each in a brainstorming session to 
clarify their interests and encourage them to think critically about research goals under 
the time constraints of their academic schedules. 
Additionally, we anticipate that sharing completed student project reports with 
future trainees will guide thinking about the scope of possible projects (Supplementary files).
